Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion

### 2023-07-15 Manuscript.Rmd
maineffects_for_within_/_across

---
title: "Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion"
author: 
  - name : "Alexandra G. Mitchell"
    affiliation : "1"
  - name : "Jesper Fischer Ehmsen"
    affiliation : "1"
  - name : "Daniel Elmstrom Christensen"
    affiliation : "2"
  - name : "Anna Villaume Stuckert"
    affiliation : "3"
  - name : "Patrick Haggard"
    affiliation : "4"  
  - name : "Francesca Fardo"
    affiliation : "1"  
affiliation:
  - id : "1"
    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University, Denmark"
  - id : "2"
    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University, Denmark"
  - id : "3"
    institution : "Departement of Neuroscience, University of Copenhagen, Denmark"
  - id : "4"
    institution : "Institute of Cognitive Neuroscience, University College London, United Kingdom"
  - id : "5"
    institution : "Danish Pain Research Center, Aarhus University, Denmark"
#date: "`r Sys.Date()`"
output:
  word_document:
  html_document: default
  pdf_document:
    latex_engine: xelatex
bibliography: knitting files/Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion.bib
link-citations: yes
linkcolor: blue
always_allow_html: yes
editor_options: 
  markdown: 
    wrap: sentence
---

@@

In keeping with the unique heat and burning features of TGI, our results exhibited a more robust TGI when stimuli were confined within dermatomes compared to when applied across dermatomes, corresponding to non-adjacent spinal segments (Fig. 2).
When rating the cold thermode (Exp. 1), participants reported a significantly reduced subjective experience of cold for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`).
However we did not observed such interaction effect for warm ($\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`) and burning ratings ($\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`).

In contrast, when rating the warm thermode (Exp. 2), participants reported markedly enhanced burning sensations for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).
However, we did not observe a modulation of cold ($\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`) ) and warm thermosensory ratings ($\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`).

>>>>

---
title: "Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion"
author: 
  - name : "Alexandra G. Mitchell"
    affiliation : "1"
  - name : "Jesper Fischer Ehmsen"
    affiliation : "1"
  - name : "Daniel Elmstrom Christensen"
    affiliation : "2"
  - name : "Anna Villaume Stuckert"
    affiliation : "3"
  - name : "Patrick Haggard"
    affiliation : "4"  
  - name : "Francesca Fardo"
    affiliation : "1"  
affiliation:
  - id : "1"
    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University, Denmark"
  - id : "2"
    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University, Denmark"
  - id : "3"
    institution : "Departement of Neuroscience, University of Copenhagen, Denmark"
  - id : "4"
    institution : "Institute of Cognitive Neuroscience, University College London, United Kingdom"
  - id : "5"
    institution : "Danish Pain Research Center, Aarhus University, Denmark"
#date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
  word_document:
bibliography: knitting files/Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion.bib
link-citations: yes
linkcolor: blue
always_allow_html: yes
editor_options: 
  markdown: 
    wrap: sentence
---

@@

In keeping with the unique heat and burning features of TGI, our results exhibited a more robust TGI when stimuli were confined within dermatomes compared to when applied across dermatomes, corresponding to non-adjacent spinal segments (Fig. 2).

When rating the cold thermode (Exp. 1), participants reported a significantly reduced subjective experience of cold for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_cold_exp1$beta[6]`, `r make_pvalue(stats_model_cold_exp1$p[6])`).

However we did not observed such interaction effect for warm ($\beta$ = `r stats_model_warm_exp1$beta[6]`, `r make_pvalue(stats_model_warm_exp1$p[6])`), but with a strong main effect of dermatome ($\beta$ = `r stats_model_warm_exp1$beta[2]`, `r make_pvalue(stats_model_warm_exp1$p[2])`)
No significant interaction nor main effect was found for the burning ratings ($\beta$ = `r stats_model_burn_exp1$beta[6]`, `r make_pvalue(stats_model_burn_exp1$p[6])`, ($\beta$ = `r stats_model_burn_exp1$beta[2]`, `r make_pvalue(stats_model_burn_exp1$p[2])`, interaction, main effect respectively).

In contrast, when rating the warm thermode (Exp. 2), participants reported markedly enhanced burning sensations for TGI, but not non-TGI, stimuli applied within a dermatome compared to across dermatomes (stimulation by dermatome interaction: $\beta$ = `r stats_model_burn_exp2$beta[6]`, `r make_pvalue(stats_model_burn_exp2$p[6])`).
However, we did not observe a modulation of cold ($\beta$ = `r stats_model_cold_exp2$beta[6]`, `r make_pvalue(stats_model_cold_exp2$p[6])`), nor main effect ($\beta$ = `r stats_model_cold_exp2$beta[2]`, `r make_pvalue(stats_model_cold_exp2$p[2])`) ) and warm thermosensory ratings ($\beta$ = `r stats_model_warm_exp2$beta[6]`, `r make_pvalue(stats_model_warm_exp2$p[6])`), also without a significant main effect of dermatome ($\beta$ = `r stats_model_warm_exp2$beta[2]`, `r make_pvalue(stats_model_warm_exp2$p[2])`).
